Talks

### 2025-03-24 talks.qmd
update

>>>>

- 25 March: The Accelerator For Innovation & Research Funding Experimentation - AFIRE @ The National Research Foundation
and Research on Research Institute Partnership Meeting: [slides](https://docs.google.com/presentation/d/1UkmQxS7nlKJA784B95NuNO_UoH6PlDl6/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)

## 2025

- 19 February: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1E_A9yS-zeZNSJ7M41t8g2l9U_5ObDcc3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
